Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
weimer pass continues

\section{Algorithm Overview}

@@

Although type constraints alone cannot always match human intuition for
fault localization problems, types still contain very useful information.
We observe that some types may be inherently suspect whenever they appear,
especially for beginner-written code. For example, there are very few
reasons to have a variable of type \lt{NoneType} in Python. We model
type information as a categorical feature. Possible
values include all the basic Python types (such as \lt{int}
and \lt{tuple}) as well as three special values:
\begin{itemize}
    \item \lt{Statement} --- Given to all statements, since our terms
    include both statments and expressions but only expressions
    have types
    \item \lt{Unknown} --- Given to expressions that are never evaluated in the dynamic
    trace
    \item \lt{Multiple} --- Given to expressions which are evaluated multiple times in
    a trace and do not always have the same type
\end{itemize}

@@

Our raw data consist of every Python 3 program that a user executed on
PythonTutor.com~\cite{Guo2013-vu} (not in ``live'' mode) during 2017, other
than those with syntax errors or undefined variables.  Each program which
crashes (throws an uncaught Python exception) is paired with the next
program (by the same user) that does not crash, under the assumption that
the latter is the fixed version of the former. We discard pairs where the
difference between crashing and fixed versions is too high (more than a
stddev above average), since these are most likely to be violations of that
assumption (i.e., the program that does not crash is unrelated to the
crashing program). We also discard submissions that are out of scope given
PythonTutor's policies (e.g., very long-running executions or the
use of forbidden libraries).

Ultimately, the dataset used in this evaluation contained just over
270,000 usable pairs of programs.

@@

Our algorithm is based on supervised machine learning and thus requires
labeled training instances. In addition, our evaluations require a ground
truth notion of which terms correspond to correct fault localizations.

We use the terms changed involved in the fixes by actual users as our
ground truth and training information.  Many PythonTutor users use the site
in an iterative fashion: they start out by writing a program that crashes,
and then edit it until it no longer crashes. Our dataset contains only
those crashing programs for which the same user later submitted a program
that did not crash. We compute a tree-diff \cite{tree-diff} between the
originaly, buggy submission and the first fixed submission. We define
the ground truth correct answer to be the set of terms in the crashing
program that also appear in the diff. We discuss the implications of this
choice in \secref{threats}.

@@

\subsection{Methodology}

For these evaluations, we employ decision trees as our machine learning
algorithm, since they provided the best accuracy on our data given the
available training time.

We report Top-1 and Top-3...

We define FIXME-ACCURACY to be FIXME.

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={Baseline,Top-1,Top-2,Top-3},
    xtick=data,
    ymin=0,
    ylabel=Model Accuracy,
    enlarge x limits=0.3,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{fault-localization-random-forest.csv};
\end{axis}
\end{tikzpicture}
\caption{Fault localization accuracy.
Baseline is the normal Python interpreter. Other bars represent
our approach, using random forests,
on the largest dataset (272534 pairs).}
\label{fig-full-dataset-acc-random-forest}
\end{figure}

We first use the full dataset to train and test decsion forests optimized for
Top-1, Top-2, and Top-3 accuracy. As shown in \figref{full-dataset-acc-random-forest},
these produce a correct answer 60, 72, and
79\% of the time (to two significant figures). As a baseline, we determine that
the expression blamed by the standard Python interpreter (i.e. the one that
causes it to crash) is only changed by the user 45\% of the time. Thus our
most directly comparable model, the one for Top-1, significantly outperforms
this baseline, and as we then exercise our power to give a ranked output rather
than a single answer, our margin gets even better.

@@

\begin{table}[]
\begin{tabular}{llc}
Name                      & Category                & Gini Importance \\ \bottomrule
P size                    & Contextual (Syntactic)  & 0.112 \\
C3 is statement           & Contextual (Syntactic)  & 0.061 \\
P is list literal         & Contextual (Syntactic)  & 0.055 \\
Program crashes here      & Dynamic (Error location)& 0.039 \\
Type is unknown           & Dynamic (Type)          & 0.037 \\
P type is unknown         & Contextual (Type)       & 0.037 \\
Err message is IndexError & Dynamic (Error message) & 0.033 \\
Size                      & Syntactic               & 0.028 \\
P is dictionary literal   & Contextual (Syntactic)  & 0.027 \\
C1 size                   & Contextual (Syntactic)  & 0.024 \\
Is variable               & Syntactic               & 0.020 \\
C1 type is unknown        & Contextual (Type)       & 0.020 \\
\toprule
\end{tabular}
\caption{Feature predictive power (for a Top-3 Decision Tree
learned on the entire dataset). P and C1-C3 refer to the parent and
first three children of the node in question.}
\label{tab-feature-predictive-power}
\end{table}

\begin{table}[]
\begin{center}
\begin{tabular}{llc}
Name                     & Category                & F-score \\ \bottomrule
C3 is statement          & Contextual (Syntactic)  & 69 \\
Size                     & Syntactic               & 63 \\
Program crashes here     & Dynamic (Error location)& 50 \\
P type is list           & Contextual (Type)       & 36 \\
C1 type is bool          & Contextual (Type)       & 30 \\
P type is unknown        & Contextual (Type)       & 28 \\
C1 is expression         & Contextual (Type)       & 25 \\
C3 size                  & Contextual (Syntactic)  & 20 \\
C1 is binary or unary op & Contextual (Syntactic)  & 20 \\
C1 size                  & Contextual (Syntactic)  & 18 \\
P type is dictionary     & Contextual (Type)       & 17 \\
Type is string           & Dynamic (Type)          & 12 \\
\toprule
\end{tabular}
\end{center}
\caption{Feature predictive power as measured by ANOVA.  The F-score in
shown in
thousands to two significant figures; all p-values are less than 0.01.}
\label{tab-anova}
\end{table}

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={No Context, No Types},
    xtick=data,
    ymin=0,
    ymax=1.1,
    ylabel=Normalized Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{removing-features-2-normalized.csv};
    \draw [red] ({rel axis cs:0,0}|-{axis cs:No Types,1}) -- ({rel axis cs:1,0}|-{axis cs:No Types,1}) node [pos=0.33, above] {};
\end{axis}
\end{tikzpicture}
\caption{Accuracy when features are removed, based on Top-1 decision trees on a
random subset of 20000 program pairs, as compared to a Top-1 decision tree trained
on all features.
\fixme{will add No Syntax bar}
}
\label{fig-removing-features}
\end{figure}

\tabref{feature-predictive-power} summarizes the relative importance
of the top features in our model. The features are ranked by their
Gini importance (or mean decrease in impurity), a common measure
for decision tree and random forest models~\cite{breiman2001random}. Informally, the
Gini importance conveys a weighted count of the number of times a feature
is used to split a node: a feature that is learned to guide more model
classification decisions is more important. Similarly, \tabref{anova} gives
an alternate view of the relative feature importances, as measured by an
analysis of variance (ANOVA).

We also present the results of a leave-one-out analysis in which
certain categories of features are removed and the model is trained
and tested only on those that remain. \figref{removing-features} shows
that there is a significant decrease in accuracy in each case. We note,
however, that leave-one-out analyses underestimate importance in cases of
feature overlap. For example, if a small program contains a string bug but
only a few string variables, both type information and slice information
are likely to implicate similar terms.

In all cases we see that syntactic, dynamic, and contextual features are
all important. Features such as FIXME, FIXME and FIXME are found to be of
primary importance. We interpret this to mean FIXME with respect to the
application of our algorithm to beginner-written code.

@@

We next try training and testing Top-1 decision trees on only the subsets of
the data
corresponding to each of the five most common exceptions: \lt{TypeError},
\lt{IndexError}, \lt{AttributeError}, \lt{ValueError}, and \lt{KeyError}.
As shown in \figref{defect-categories}, these models have accuracy between
86\% and 115\% of a comparable model trained on the data as a whole. This shows
that our algorithm is robust, able to give high accuracy fault localizations on
a wide variety of defect types.

@@

To demonstrate that our evaluation dataset is not only larger but also more
diverse than those used in previous work, we compare the diversity of
programs present here to those in a relevant balance. The Nate
algorithm~\cite{learning-to-blame} also provides type error localization
and also focuses on a machine-learning approach backed by slicing. However,
Nate targets strongly statically typed OCaml programs. Nate's evaluation
also focused on beginner-written programs: specifically, it considered
student submissions to 23 different university homework problems.  Thus the
Nate dataset is comparatively homogeneous, raising concerns about whether
evaluation results would generalize to more diverse settings.

@@

\figref{diversity} shows the results of clustering on our dataset and the
Nate dataset. At a high level, the structural similarity in the graphs
confirms the comparability of cluster counts between the two datasets.  For
all values of the inconsistency threshold, there are more clusters in our
Python dataset than in the baseline OCaml dataset. This suggests that our
dataset contains a more diverse set of programs. Note that we are not
claiming any novelty or advances in clustering accuracy in this
determination (indeed, scalability concerns limited us to coarser
approaches); instead, our claim is that even with simple clustering,
it is clear that our dataset contains a greater diversity of programs than
were considered by previously-published evaluations.
We view it as an advantage of our algorithm that it can apply to multiple
different program categories.

@@

\fixme{
Pick out one example where we did poorly. Walk through why it is ``out of
scope'', in some sense: we would need features that capture XYZ to handle
it correctly, but those are either expensive or undecideable. Hint at
future work.
}

@@

\begin{figure}
\begin{lstlisting}
areaCodes = [800, 555]
for i in range(0, len(areaCodes) + 1):
    print(areaCodes[i])
\end{lstlisting}
\caption{A program with an off-by-one bug.}
\label{fig-win-example-two}
\end{figure}

We now go through a couple examples where our method does well. These examples
are adapted slightly for simplicity of
presentation and to protect the anonymity of the programmers, but they retain
the essential character of the originals from our dataset.

\paragraph{NoneType}
The function in \figref{win-example-one} attempts to remove all vowels from a
given word. However the
\lt{remove} method in line 7 actually modifies the list in place and returns
\lt{None}, so the correct version forgoes the assignment and just has
\lt{w_list.remove(letter)}. Python does not crash until line 8, where its
message is \lt{TypeError: can only join an iterable}. However, our decision
tree flags the correct statement, using as some of its rules that it is an
assignment statement whose second child has type \lt{NoneType}. This seems to
capture the intuitive rule that there is rarely a good reason to assign the
value \lt{None} to a variable. Note that these rules use both the syntactic
form of the statement (an assignment) and the dynamic type of one of its
children, so all our categories of features - syntactic, dynamic, and
contextual - were useful here.

\paragraph{Off-by-one bugs}
In \figref{win-example-two}, the programmer incorrectly adds one to the high
end of their range, causing an \lt{IndexError: list index out of range} on line
3 during the final iteration of the for loop. The correct expression to blame
is the addition \lt{len(areaCodes) + 1}. Some of the rules that our
decision tree uses to correctly localize this bug include that the error is an
index error, the type of the parent, and the fact that it's an addition
expression. Thus once again we see all three categories of features being used.

>>>>

\section{Algorithm Overview}
\label{sec-algorithm}

@@

Although type constraints alone cannot always match human intuition for
fault localization problems, types still contain very useful information.
We observe that some types may be inherently suspect whenever they appear,
especially for beginner-written code. For example, there are very few
reasons to have a variable of type \lt{NoneType} in Python. We model
type information as a categorical feature. Possible
values include all the basic Python types (such as \lt{int}
and \lt{tuple}) as well as three special values:
\begin{itemize}
    \item \lt{Statement} --- Given to all statements, since our terms
    include both statements and expressions but only expressions
    have types
    \item \lt{Unknown} --- Given to expressions that are never evaluated in the dynamic
    trace
    \item \lt{Multiple} --- Given to expressions which are evaluated multiple times in
    a trace and do not always have the same type
\end{itemize}

@@

Our raw data consist of every Python 3 program that a user executed on
PythonTutor.com~\cite{Guo2013-vu} (not in ``live'' mode) during 2017, other
than those with syntax errors or undefined variables.  Each program which
crashes (throws an uncaught Python exception) is paired with the next
program (by the same user) that does not crash, under the assumption that
the latter is the fixed version of the former. We discard pairs where the
difference between crashing and fixed versions is too high (more than a
stddev above average), since these are most likely to be violations of that
assumption (i.e., the program that does not crash is unrelated to the
crashing program). We also discard submissions that are out of scope given
PythonTutor's policies (e.g., very long-running executions or those that 
use forbidden libraries).

Ultimately, the dataset used in this evaluation contained 
272,534 usable pairs of programs.

@@

Our algorithm is based on supervised machine learning and thus requires
labeled training instances.  For these experiments, we employ a random
forest our machine learning algorithm, finding it to provide the best
accuracy on our dataset with a scalable training and testing time.  In
addition, our evaluations require a ground truth notion of which terms
correspond to correct fault localizations.

We use the terms changed involved in the fixes by actual users as our
ground truth and training information.  Many PythonTutor users use the site
in an iterative fashion: they start out by writing a program that crashes,
and then edit it until it no longer crashes. Our dataset contains only
those crashing programs for which the same user later submitted a program
that did not crash. We compute a tree-diff~\cite{tree-diff} between the
originaly, buggy submission and the first fixed submission. We define
the \emph{ground truth} correct answer to be the set of terms in the
crashing program that also appear in the diff. We discuss the implications
of this choice in \secref{threats}.

Given that notion of ground truth, a candidate fault localization answer is
\emph{accurate} if it is contained in the ground truth set. That is, if the
human user changed lines $X$ and $Y$, a technique (either our algorithm 
or a baseline) is given credit for returning either $X$ or $Y$. When
considering ranked lists, a response list is \emph{top-$k$ accurate} if any one
of the top $k$ answers is contained in the ground truth set. \fixme{Read
this paragraph and correct it for truth; it is currently simply WRW's best
guess and I don't actually know what you did.}

@@

@@

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={Baseline,Top-1,Top-2,Top-3},
    xtick=data,
    ymin=0,
    ylabel=Model Accuracy,
    enlarge x limits=0.3,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{fault-localization-random-forest.csv};
\end{axis}
\end{tikzpicture}
\caption{Fault localization accuracy.
Baseline is the normal Python interpreter. The Top-$k$ bars represent
our approach, using random forests,
on the largest dataset (272534 pairs). The strong performance of our
algorithm on a large, real-world dataset is the primary result of this paper. 
}
\label{fig-full-dataset-acc-random-forest}
\end{figure}

We first use the full dataset to train and test decision forests optimized for
Top-1, Top-2, and Top-3 accuracy. As shown in \figref{full-dataset-acc-random-forest},
these produce a correct answer 60\%, 72\%, and
79\% of the time (to two significant figures). As a baseline, we determine that
the expression blamed by the standard Python interpreter (i.e., the one that
raises the uncaught exception) is only changed by the user 45\% of the
time.

Thus, our most directly comparable model (Top-1), significantly outperforms
this baseline. Users who are only willing to look at a single error message
would have been better-served by our Top-1 model on this historical data.

In addition, previous studies have shown that developers are willing to use
very short ranked lists~\cite[Sec.~5.6]{orso-parnin}, but not voluminous
ones. Our Top-3 model accuracy of 79\% dramatically improves upon the
current state of practice for scalable type-error localization in Python.

@@

\begin{table}[]
\begin{tabular}{llc}
Name                      & Category                & Gini Importance \\ \bottomrule
Parent size                    & Contextual (Syntactic)  & 0.112 \\
Child3 is statement           & Contextual (Syntactic)  & 0.061 \\
Parent is list literal         & Contextual (Syntactic)  & 0.055 \\
Program crashes here      & Dynamic (Error location)& 0.039 \\
Type is unknown           & Dynamic (Type)          & 0.037 \\
Parent type is unknown         & Contextual (Type)       & 0.037 \\
Err message is IndexError & Dynamic (Error message) & 0.033 \\
Size                      & Syntactic               & 0.028 \\
Parent is dictionary & Contextual (Syntactic)  & 0.027 \\
Child1 size                   & Contextual (Syntactic)  & 0.024 \\
Is variable               & Syntactic               & 0.020 \\
Child1 type is unknown        & Contextual (Type)       & 0.020 \\
\toprule
\end{tabular}
\caption{Feature predictive power (for a Top-3 Decision Tree
learned on the entire dataset). Parent and Child1--3 refer to the parent and
first three children of the node in question.}
\label{tab-feature-predictive-power}
\end{table}

\begin{table}[]
\begin{center}
\begin{tabular}{llc}
Name                     & Category                & F-score \\ \bottomrule
Child3 is statement          & Contextual (Syntactic)  & 69 \\
Size                     & Syntactic               & 63 \\
Program crashes here     & Dynamic (Error location)& 50 \\
Parent type is list           & Contextual (Type)       & 36 \\
Child1 type is bool          & Contextual (Type)       & 30 \\
Parent type is unknown        & Contextual (Type)       & 28 \\
Child1 is expression         & Contextual (Type)       & 25 \\
Child3 size                  & Contextual (Syntactic)  & 20 \\
Child1 is binary or unary op & Contextual (Syntactic)  & 20 \\
Child1 size                  & Contextual (Syntactic)  & 18 \\
Parent type is dictionary     & Contextual (Type)       & 17 \\
Type is string           & Dynamic (Type)          & 12 \\
\toprule
\end{tabular}
\end{center}
\caption{Feature predictive power as measured by ANOVA.  The F-score in
shown in
thousands to two significant figures; all p-values are less than 0.01.
Parent and Child1--3 refer to the parent and first three children of
the node in question.}
\label{tab-anova}
\end{table}

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
    ybar,
    symbolic x coords={No Context, No Types},
    xtick=data,
    ymin=0,
    ymax=1.1,
    ylabel=Normalized Model Accuracy,
    enlarge x limits=0.5,
    legend style={at={(0.5,-0.15)},anchor=north}
]
    \addplot table[x=scoreName, y=score, col sep=comma]{removing-features-2-normalized.csv};
    \draw [red] ({rel axis cs:0,0}|-{axis cs:No Types,1}) -- ({rel axis cs:1,0}|-{axis cs:No Types,1}) node [pos=0.33, above] {};
\end{axis}
\end{tikzpicture}
\caption{Normalized accuracy when categories of features are removed, based
on Top-1 decision trees on a random subset of 20,000 program pairs, as
compared to a Top-1 decision tree trained on all features.
\fixme{will add No Syntax bar}
}
\label{fig-removing-features}
\end{figure}

Having established the efficacy of our approach, we now investigate which
elements of our algorithmic design (\secref{algorithm}) contributed to that
success. 
\tabref{feature-predictive-power} summarizes the relative importance
of the top features in our model. The features are ranked by their
Gini importance (or mean decrease in impurity), a common measure
for decision tree and random forest models~\cite{breiman2001random}. Informally, the
Gini importance conveys a weighted count of the number of times a feature
is used to split a node: a feature that is learned to guide more model
classification decisions is more important. Similarly, \tabref{anova} gives
an alternate view of the relative feature importances, as measured by a
standard analysis of variance (ANOVA).

Some features, such as ``program crashes here'' and features
related to term size, are fairly direct. Others, such as ``Child3 is
statement'', a contextual, syntactic feature that was found to be very
important, merit additional explanation. In practice, we found it to
encode FIXME, since Python terms with statements in the third child node
position are FIXME. Similarly, features that determine if the parent node
is a list or dictionary are relevant because of FIXME. In beginner-written
Python we find that defects and typos often in the immediate child position
of a list or dictionary term because of FIXME. Finally, we note the
importance of our \lt{Unknown} type feature for expressions that are never
evaluated in the given trace: we find that they are relevant because of
FIXME. \fixme{Ben (etc.) must actually fill in real explanations here.}

More broadly, we also present the results of a leave-one-out analysis in which
entire categories of features are removed and the model is trained
and tested only on those that remain. \figref{removing-features} shows
that there is a significant decrease in accuracy in each case. We note,
however, that leave-one-out analyses underestimate importance in cases of
feature overlap. For example, if a small program contains a string bug but
only a few string variables, both type information and slice information
are likely to implicate similar terms.

In all cases we see that syntactic, dynamic, and contextual features (i.e.,
the design decisions of our algorithm) are crucial to our algorithm's
accuracy.

@@

We investigate the sensitivity of our algorithm to different categories of
Python errors: is our accuracy sensitive to certain kinds of user defects? 
We investigate training and testing Top-1 decision trees on only those
subsets of the dataset corresponding to each of the five most common
uncaught exceptions: \lt{TypeError}, \lt{IndexError}, \lt{AttributeError},
\lt{ValueError}, and \lt{KeyError}. Together, these five exceptions make
up FIXME\% of the errors in our dataset.

As shown in \figref{defect-categories}, these per-defect models have
normalized accuracy between 86\% and 115\% of a comparable model trained on
the dataset as a whole. This shows that our algorithm is robust and able to
give high-accuracy fault localizations on a wide variety of defect types. 
Having consistent, rather than defect-type-sensitive, performance is
important for debugging-tool
usability~\cite{orso-parnin,Bessey2010,ayewah10}.

@@

To demonstrate that our evaluation dataset is not only larger but also more
diverse than those used in previous work, we compare the diversity of
programs used here to those in a relevant baseline. The Nate
algorithm~\cite{learning-to-blame} also provides type error localization
and also focuses on a machine-learning approach backed by slicing. However,
Nate targets strongly statically typed OCaml programs. Nate's evaluation
also focused on beginner-written programs: specifically, it considered
student submissions to 23 different university homework problems.  Such a
dataset is comparatively homogeneous, raising concerns about whether
associated evaluation results would generalize to more diverse settings.

@@

\figref{diversity} shows the results of clustering on our dataset and the
Nate dataset. At a high level, the structural similarity in the graphs
confirms the comparability of cluster counts between the two datasets.  For
all values of the inconsistency threshold, there are more clusters in our
Python dataset than in the baseline OCaml dataset. This suggests that our
dataset contains a more diverse set of programs. Note that we are not
claiming any novelty or advances in clustering accuracy in this
determination (indeed, scalability concerns limited us to coarser
approaches); instead, our claim is that even with simple clustering,
it is clear that our dataset contains a greater diversity of programs, even
when controlling for size, than were considered by previously-published
evaluations. We view it as an advantage of our algorithm that it can apply
to multiple different program categories.

@@

@@

We now highlight a few indicative localization examples in detail to
demonstrate how our algorithm accurately localizes faults. 
These examples are simplified slightly for presentation and to protect the
anonymity of the programmers, but they retain the essential character of
the originals from our dataset.

\paragraph{NoneType}
The function in \figref{win-example-one} attempts to remove all vowels from
a given word. However the \lt{remove} method in line 7 actually modifies
the list in place and returns \lt{None}. By contrast, the user-corrected
version forgoes the assignment instead uses \lt{w_list.remove(letter)}. In
the buggy case, Python does not crash until line 8, where its message is
the somewhat-misleading \lt{TypeError: can only join an iterable}. However,
our decision tree flags the correct statement, based on the features 
that it is an assignment statement whose second child has type
\lt{NoneType}. This seems to capture the intuitive reasoning that there is
rarely a good reason to assign the value \lt{None} to a variable.

Note that our algorithm uses both the syntactic form of the statement (an
assignment) and the dynamic type of one of its children, so all our
categories of features --- syntactic, dynamic, and contextual --- were
useful here.

\begin{figure}
\begin{lstlisting}
areaCodes = [800, 555]
for i in range(0, len(areaCodes) + 1):
    print(areaCodes[i])
\end{lstlisting}
\caption{A program with an off-by-one bug on line 2.}
\label{fig-win-example-two}
\end{figure}

\paragraph{Off-by-one bugs}
In \figref{win-example-two}, the programmer incorrectly adds one to the high
end of their range, causing an \lt{IndexError: list index out of range} on line
3 during the final iteration of the for loop. The correct expression to blame
is the addition \lt{len(areaCodes) + 1}. Some of the features that our
decision tree uses to correctly localize this bug include that the error is an
index error, the type of the parent, and the fact that it is an addition
expression. This example also highlights the use of all three categories of
features simultaneously to capture a notion of root cause that more closely
aligns with human expectations.
